Location and Scale-Invariant Power Transformations for Transforming Data to

### 2025-10-28 manuscript_rmarkdown/manuscript.Rmd
Update discussion and caption for figure 5.

For each sequence, the p-value for the respective test was used to reject the null
hypothesis that the sequence is (centrally) normal. The null hypothesis was rejected if $p \leq 0.05$.
The type I error rate was determined by computing the fraction of centrally normal sequences rejected this way.
Figure \ref{fig:empirical-central-normality-error_rate} shows that when the estimated outlier rate 
for the empirical central normality test matches the outlier rate in the data,
the test yields an accurate Type I error rate.
The Shapiro-Wilk test is overly conservative in the presence of any outliers. 
Empirical central normality tests where the estimated outlier rate is lower
than the actual outlier rate are likewise conservative, but to a lesser degree. 
Empirical central normality tests where the estimated outlier rate is higher 
than the actual outlier rate are optimistic.

```{r empirical-central-normality-error_rate, warning=FALSE, message=FALSE, fig.cap=cap, fig.height=2.5}
cap <- paste0(
  "Observed type I error rates for central normality tests in the presence of data sampled from normal distributions ",
  "without outliers, or with a 5% or 10% outlier rate. ",
  "The empirical central normality (ECN) test used $\\kappa = 0.80$, and was further parameterised by the ",
  "estimated outlier rate $\\zeta = 0.00$ (ECN (0 %)), $\\zeta = 0.05$ (ECN (5 %)) and $\\zeta = 0.10$ (ECN (10%))."  
)

>>>>

For each sequence, the p-value for the respective test was used to reject the null
hypothesis that sequences were derived from a population with a (central) normal distribution.
The null hypothesis was rejected if $p \leq 0.05$.
The type I error rate was determined by computing the fraction of sequences rejected this way.
Figure \ref{fig:empirical-central-normality-error_rate} shows that when the
central portion $\kappa$ of the central normal distribution is equal or greater
than the $\kappa$ parameter for the empirical central normality test, the tests 
are accurate. If $\kappa$ of the empirical central normality test exceeds that 
the central portion $\kappa$ for the underlying distribution, 
tests are conservative. The Shapiro-Wilk test behaves similar to the empirical
central normality test with $\kappa = 1.0$, which is expected. For $n < 10$,
the empirical central normality test can be optimistic.

```{r empirical-central-normality-error_rate, warning=FALSE, message=FALSE, fig.cap=cap, fig.height=2.5}
cap <- paste0(
  "Observed type I error rates for central normality tests in the presence of data sampled from ",
  "central normal distributions with $\\kappa \\in \\left{0.6, 0.8, 1.0\\right}$. ",
  "Three empirical central normality (ECN) tests were performed, parameterised with same value for the central portion $\\kappa$. ",
  "Additionally, the Shapiro-Wilk test was assessed.",
  "ECN: empirical central normality"
)
